---
title: "EUSILC DATA EXPLORATION"
author: "Roland NGOUYAMSA"
date: "1/22/2020"
output: html_document
---

## Exploratory data analysis

Basic descriptive statistics of the dataset


#### Getting meaningful variables to segregate LOC, EU citizens from Foreign citizens.
The 2 variables of interest here are PB220A (status: Loc, EU or Foreign), PB020 (Country of survey)


```{r setup, include=FALSE}

library(dplyr)
library(ggplot2)
library(magrittr)
library(tidyr)
library(purrr)
library(vtree)
library(knitr)

source("getdata.R")

#library(MASS)


datap <- get_data(vect = pfiles, vars = pvar)

#datah <- get_data(vect = hfiles, vars = hvar)


datap <- datap %>% mutate(HB030=as.numeric(strtrim(PB030,nchar(PB030)-2)))

#data <- full_join(datap, datah, by="HB030")



head(datah)
head(datap)

#df <- datap %>% group_by(PB010, PB020, HB030) %>% summarise(count=n()) %>% tbl_df

#head(df)


```


### Summary statistics

Individual countper household

```{r}

datap %>% group_by(PB010, PB020, PB030, HB030) %>% summarise(count=n())

```




```{r}

datap %>% group_by(is.na(PY200G)) %>% summarise(count=n(),median(PY200G, na.rm = T))

datah %>% group_by(is.na(HY022)) %>% summarise(count=n(),median(HY022, na.rm = T))

datah %>% group_by(is.na(HY023)) %>% summarise(count=n(),median(HY023, na.rm = T))

datah %>% group_by(is.na(HY020)) %>% summarise(count=n(),median(HY020, na.rm = T))

```



Counts per group per country in EUSILC Sample

```{r }

counts <- table(datap$PB020, datap$PB220A)

counts

```

### Proportion as a total in EU

```{r pressure, echo=FALSE}

datap %>% group_by(PB220A) %>% summarise(counts=n()) %>% arrange(desc(counts))

```

```{r}

datap %>% group_by(PB020,PB220A) %>% summarise(counts=n()) %>% arrange(desc(counts), .by_group=TRUE)



datap %>% group_by(PB020) %>% vtree("PB220A")


vtree(datap, "PB220A")

```
